decompr: trade flow decomposition for Global Value Chain analysis

### 2014-12-03 README.Rmd
add data format figure
update examples using v 2

@@

```{r data-dimensions}
dim(intermediate_demand) # (2 + GN + totals) x (2 + GN)
dim(final_demand)        # (2 + GN + totals) x (2 + G*5)
```

Note thata **G** and **N** are automatically inferred by decompr from the dimensions of the data set.

When importing data, be sure to specify **stringsAsFactors = FALSE** and to **header=FALSE**,
as the Input-Output tables use two header lines (country and industry), e.g:

```{r manual-import, eval=FALSE}
final_demand <- read.csv( file             = "final_demand.csv",
                          header           = FALSE,
                          stringsAsFactors = FALSE               )

```

@@

```{r load_tables}
elements <- load_tables( x = intermediate_demand,
                         y = final_demand         )
```

@@

```{r wwz-wrapper}
wwz2 <- decomp( x = intermediate_demand,
                y = final_demand,
                method = "wwz"           )
```

@@

```{r source-wrapper}
source2 <- decomp( x = intermediate_demand,
                y = final_demand,
                method = "source"           )
```

>>>>

![Data format](figures/data_format.png)

@@

```{r data-dimensions}
length(region_names)        # G
length(industry_names)      # N
dim(   intermediate_demand) # (GN + totals) x GN
dim(   final_demand)        # (GN + totals) x G*5
length(output)              # GN
```

@@

The first step is to load the data and create the elements, there are all stored in a list (of class **decompr**).

```{r load_tables}
elements <- load_tables_vectors( x = intermediate_demand,
                                 y = final_demand,
                                 k = region_names,
                                 i = industry_names,
                                 o = output               )
```

@@

```{r wwz-wrapper}
wwz2 <- decomp( x = intermediate_demand,
                y = final_demand,
                k = region_names,
                i = industry_names,
                o = output ,
                method = "wwz"           )
```

@@

```{r source-wrapper}
source2 <- decomp( x = intermediate_demand,
                   y = final_demand,
                   k = region_names,
                   i = industry_names,
                   o = output ,
                   method = "source"           )
```
